Colorimetric Detection of pH Strips

### 2017-12-29 code/paper/paper.tex
restructure repo

\centering
\includegraphics[height=2.5in]{SVM/SVM_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for SVM model. The confusion matrix plots the predicted class on the X axis, and the true class on the Y axis. Therefore, elements along the diagonal of the matrix were predicted correctly. In this case, 2 of 27 images were misclassified.}
\label{svm_confusion}
\end{figure}

@@

\centering
\includegraphics[height=2.5in]{LDA/LDA_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for LDA model. None of the images were misclassified in this fold.}
\label{lda_confusion}
\end{figure}

@@

\centering
\includegraphics[height=2.5in]{KNN_clf_noPCA/KNN_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for kNN model (without PCA/scaling). 2 of 35 images were misclassified.}
\label{knn_confusion}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{Ridge/ridge_regression3.png}
\caption{Ridge Regression Model. The Y axis is the Mean Squared Error ($\frac{1}{n} \Sigma_{i=1}^n (Y_i - \hat(Y)_i)^2$, where $Y_i$ is the true value and $\hat(Y)_i$ is the predicted value from our model) and the X axis is different levels of regularization on the model, shown on a logarithmic scale from -3 to 1. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{ridge}
\end{figure}

>>>>

\centering
\includegraphics[height=2.5in]{SVM/SVM_classification_cfm.png}
\caption{Sample confusion matrix for one fold of three-fold cross validation for SVM model. The confusion matrix plots the predicted class on the X axis, and the true class on the Y axis. Therefore, elements along the diagonal of the matrix were predicted correctly. In this case, 2 of 27 images were misclassified.}
\label{svm_confusion}
\end{figure}

@@

\centering
\includegraphics[height=2.5in]{LDA/LDA_classification_cfm.png}
\caption{Sample confusion matrix for one fold of three-fold cross validation for LDA model. None of the images were misclassified in this fold.}
\label{lda_confusion}
\end{figure}

@@

\centering
\includegraphics[height=2.5in]{KNN_clf_noPCA/KNN_classification_cfm.png}
\caption{Sample confusion matrix for one fold of three-fold cross validation for kNN model (without PCA/scaling). 2 of 35 images were misclassified.}
\label{knn_confusion}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{Ridge/ridge_regression3.png}
\caption{Ridge Regression Model. The Y axis is the Mean Squared Error, which is $\frac{1}{n} \Sigma_{i=1}^n (Y_i - \hat{Y}_i)^2$ where $Y_i$ is the true value of strip $i$ and $\hat{Y}_i$ is the predicted value from our model of strip $i$, and the X axis is different levels of regularization on the model, shown on a logarithmic scale from $-3$ to $1$. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{ridge}
\end{figure}
